Model

### 2020-02-20 stats/model.Rmd
update model analysis file

```{r}
plot_mixture_dmm <- ggplot(mixture_dmm, aes(x = value, fill = factor(chain)))+
  geom_density(alpha = 0.3)+
  xlab("value")+
  facet_grid(~type)+
  xlim(0,1)+
  theme_few()

@@

@@

@@

com_global_params <- bind_rows(
  global_params%>%mutate(model="pragmatic"),
  global_params_fb%>%mutate(model="fullBayes"),
  global_params_mm%>%mutate(model="mixture")
)

ggplot(com_global_params, aes(x = value, fill = model, group = paste(model,chain)))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(type ~ parameter, scales = 'free')+
  theme_few()+
  theme(legend.position = "bottom")

@@

```{r}
ggsave("../graphs/item_params_by_model.pdf", width = 8, height = 3, scale = 1.5)
```

>>>>

```{r}
plot_mixture_dmm <- ggplot(mixture_dmm, aes(x = value, fill = factor(chain)))+
  geom_density(alpha = 0.3)+
  xlab("value")+
  facet_grid(~type)+
  theme_few()

@@

x_dmm <- sample(1:length(unique(mixture_dmm$iteration)), 200)

plot_mixture_line <- mixture_dmm%>%
  filter(iteration %in% x_dmm) %>%
  spread(type, value) %>%
  expand_grid(.,age = unique(data_comb$age)) %>%
  mutate(mixture = plogis(intercept + slope * age))

ggplot() +
  geom_line(data = plot_mixture_line, aes(x=age+2,y = mixture, col = factor(chain), group = interaction(chain,iteration)),size = .2, alpha = .1)+
  labs(x="Age",y="Mixture (proportion me inference)")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F, fill = F)
```

@@

## Likelihood

```{r}
like_chain <- readRDS("../saves/expl_model_likelihood_chain.rds")

model_comp <- readRDS("../saves/expl_model_comparison.rds")%>%
  mutate(BF = format(round(exp(logBF)),scientific=F))
```

@@

com_global_params <- bind_rows(
  global_params%>%mutate(model="pragmatic"),
  global_params_fb%>%mutate(model="fullBayes"),
  global_params_mm%>%mutate(model="mixture"),
  global_params_dmm%>%mutate(model="mixture_dev")
)

ggplot(com_global_params, aes(x = value, fill = model, group = paste(model,chain)))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(type ~ parameter, scales = 'free')+
  theme_few()+
  theme(legend.position = "bottom")+
  scale_fill_ptol()

@@

```{r}
ggsave("../graphs/global_params_by_model.pdf", width = 8, height = 3, scale = 1.5)
```

### Prior parameters

x_prior <- sample(1:length(unique(com_global_params$iteration)), 200)

plot_prior_line <- com_global_params%>%
  filter(parameter == "prior")%>%
  filter(iteration %in% x_prior) %>%
  spread(type, value) %>%
  expand_grid(.,age = unique(data_comb$age)) %>%
  mutate(prior = plogis(intercept + slope * age))

ggplot() +
  geom_line(data = plot_prior_line, aes(x=age+2,y = prior, col = model, group = interaction(chain,iteration)),size = .2, alpha = .1)+
  labs(x="Age",y="Prior")+
  theme_few() +
  facet_grid(~model)+
  ylim(-0.05,1.05)+
  xlim(2,5)+
  scale_color_ptol()+
  guides(alpha = F, fill = F, col = F)
```
